Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-08-04 WRITEUP/ms.tex
ready to send DR

We derive the stellar mass of RXJ1131 by
fitting SED models to the rest-frame UV-to-mm photometry   % original version: UV to IR; high-z UV to radio
using the high-$z$ version of the {\sc magphys} code \citep{Magphys08a,Magphys15a}.
Two sets of stellar templates  modeled using either the \citet{BC03a} or the unpublished
Charlot \& Bruzual 2007 stellar population synthesis code
are provided in the {\sc magphys} package.
We adopt the former set.
To minimize contaminations from the quasar, we only fit to the {\it HST}, {\it Herschel}, and PdBI data,
where both the {\it HST} and the PdbI 2\,mm photometry are de-blended from the AGN
(see bottom section of \Tab{photometry}).
The input photometry are corrected for lensing using their respective magnification factors
to account for differential lensing.
We thus find a stellar mass of $M^*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
is the median value of the posterior probability distribution and
the uncertainties are derived from the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles.
We note that the models are over-fitted with a best-fit $\chi^2$\eq0.41
which is unsurprising due to sparse sampling of the SED
compare to the number of free parameters.
The resulting dust mass and \LIR are consistent with those obtained
from the MBB$+$power-law models within the uncertainties, albeit some differences
in the assumptions behind the two methods.
The consistency may be attributed to the large uncertainties arising from the lack of photometric constraints on the models and the fact that the best-fit parameters from the MBB method are similar to those of the \ncode{magphys} method.
%  Mdust 8.427   8.522   8.617
% Ldust  1.191E+001  1.204E+001  1.219E+001; but from 3-1000 \micron; should compare with our \LIR.
%
% Salpeter M* ~ 1.8 * Chabrier
% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time of $M^*$$/$SFR\ssim440 Myr for RXJ1131.

% -------
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
\caption{SEDs of RXJ1131 at $z$\eq0.654 and its lensing galaxy at $z$\eq0.295.
The photometry data (colored markers) are not corrected for lensing (see \Tab{photometry}).
Best-fit SED models of the thermal dust emission towards RXJ1131
are obtained assuming a MBB$+$power-law model.
The dashed (solid) line corresponds to a model with (without) MIR constraint at 24\,$\micron$, respectively.
\label{fig:SED}}
\end{figure}

>>>>

We derive the stellar mass of RXJ1131 by
fitting SED models to the rest-frame UV-to-mm photometry   % original version: UV to IR; high-z UV to radio
using the high-$z$ version of the {\sc magphys} code \citep{Magphys08a,Magphys15a}.
Two sets of stellar templates  modeled using either the \citet{BC03a} or the unpublished
Charlot \& Bruzual 2007 stellar population synthesis code
are provided in the {\sc magphys} package.
We adopt the former set.
To minimize contaminations from the quasar, we only fit to the {\it HST}, {\it Herschel}, and PdBI data,
where both the {\it HST} and the PdbI 2\,mm photometry are de-blended from the AGN
(see bottom section of \Tab{photometry}).
The input photometry are corrected for lensing using their respective magnification factors
to account for differential lensing (light blue circles in \Fig{SED}).
We thus find a stellar mass of $M^*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
is the median value of the posterior probability distribution and
the uncertainties are derived from the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles.
We note that the models are over-fitted with a best-fit $\chi^2$\eq0.41
which is unsurprising due to sparse sampling of the SED
compare to the number of free parameters.
The resulting dust mass and IR luminosity are consistent with those obtained
from the MBB$+$power-law models within the uncertainties, albeit some differences
in the assumptions behind the two methods.
The consistency may be attributed to the large uncertainties arising from the lack of photometric constraints on the models and the fact that the best-fit parameters from the MBB method are similar to those of the \ncode{magphys} method.
%  Mdust 8.427   8.522   8.617
% Ldust  1.191E+001  1.204E+001  1.219E+001; but from 3-1000 \micron; should compare with our \LIR.
%
% Salpeter M* ~ 1.8 * Chabrier
% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time of $M^*$$/$SFR\ssim440 Myr for RXJ1131.

% -------
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
\caption{SEDs of the host galaxy of RXJ1131 at 
$z_{\rm CO}$\eq0.654 and of the lensing galaxy at $z$\eq0.295.
The photometry data (colored markers) are listed in \Tab{photometry}, except for those
shown in light blue circles, which are corrected for lensing magnification (see \Sec{SED}).
Assuming an MBB$+$power-law model for the thermal dust emission towards RXJ1131,
the dashed (dashed-dotted) line corresponds to the best-fit model 
with (without) MIR constraint at 24\,$\micron$.
The solid black line shows the best-fit SED model with dust attenuation (light blue solid line)
obtained using the \ncode{magphys} code.
\label{fig:SED}}
\end{figure}
